\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2013-01-05 paper/mswp2012-proposal.tex
11. implications and risks

\note{
\begin{itemize}
\item {\em Length: 1-2 pages}
\item Importance of the expected results for the discipline
	\begin{itemize}
	\item     To what extent does the proposed research address important challenges?
	\end{itemize}
\item Importance of the expected results for other areas
\item What are possible risks of the project and how can they be alleviated?
	\begin{itemize}
	\item     What factors could lead to a failure of the project?
	\item     Which factors or persons could support the project and increase the chance for success?
	\item     What if important team members leave the project?
	\end{itemize}
\end{itemize}
}

>>>>

%\note{
%\begin{itemize}
%\item {\em Length: 1-2 pages}
%\item Importance of the expected results for the discipline
%	\begin{itemize}
%	\item     To what extent does the proposed research address important challenges?
%	\end{itemize}
%\item Importance of the expected results for other areas
%\item What are possible risks of the project and how can they be alleviated?
%	\begin{itemize}
%	\item     What factors could lead to a failure of the project?
%	\item     Which factors or persons could support the project and increase the chance for success?
%	\item     What if important team members leave the project?
%	\end{itemize}
%\end{itemize}
%}

\subsection{Importance of the expected results}

The main challenge to overcome with this project is to motivate people to live healthier. As we try to combine modern techniques with approved health care measures we hope to encourage the user to utilize the system as often as possible. This should lead to concrete health improvements of each individual user. The research part of the project shall lead to ground-breaking findings in the section of user interface design for ubiquitous technical health case assistants.
As there is currently no comparable system, by means of dimension, the possible target group of users is very big.

Not only individuals shall benefit from the results of our project, but whole communities. Healthier people lead to long-term savings in health care expenditures. States and health insurance funds will be able to save a lot of investments.

\subsection{Possible risks}

\subsubsection{Failure risks}
One possible failure risk is the drop-out of team members during project runtime. This is discussed in detail in section \ref{p:members_leave_project}.

As in most projects, the cancellation of funding by the investors can lead to failure or at least to a temporary stop of the project.

Another possible risk is the research and development going into a wrong direction without getting recognized for a long time. Weekly jour fixes of all important project members and rigorous compliance with the quality assurance specifications shall overcome this risk. The quality manager plays an important role in this possible failure scenario.

\subsubsection{Possible project support}
The project team shall not define itself as a "closed circuit" but accept support from outside where it makes sense. If possible, contributors of similar projects, products, etc. can get involved into the research and development of the project.

As the project proceeds and a more and more presentable solution evolves, other possible investors or contributors could be acquired. For the time being the public blog of the project can be used to communicate project success to the public, maybe later it is possible to practice a more extensive use of public relation tools an mechanisms to inform as many people as possible about the project.

% team members leave the project
\subsubsection{Risk of team members leaving the project}
\label{p:members_leave_project}
The actions to take when a team member leaves the project derive from section \ref{sect:team}. The quality assurance defines measures such as
\begin{itemize}
\item reviews,
\item weekly jour fixes,
\item extensive documentation of all work done within the project and
\item tool support for intra-project communication.
\end{itemize}
These measures shall lead to a distribution of knowledge to as many team members as possible, so that no team member can get irreplaceable and project success can't get endangered by the drop out of a single person. The quality manager is responsible for controlling and reviewing the adherence of the quality assurance specifications.

However, important team roles get back-upped by a second person. These are
\begin{itemize}
\item project manager,
\item quality manager and
\item security expert.
\end{itemize}
